Rough Draft of Supplemental Material

### 2016-02-15 supplemental/supp.tex
added the rest of the contour compare figures to supplement

\title{Rough Draft of Supplemental Material}
\author{Bradley Hintze}
\date{November 2014}
\maketitle
\tableofcontents

\newpage
\input{residuecounts}
\newpage
\input{frequency}
\newpage
\input{chis_and_angles}
\newpage
%\input{pdbchains}

>>>>

\title{Rough Draft of Supplemental Material}
\author{Bradley Hintze}
\date{January 2015}
\maketitle
\tableofcontents

\newpage
\input{residuecounts}
\newpage
\section{Top500 vs. Top8000 Reference Contours}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.75\textwidth]{contour_compare_sup}
  \caption{Areas in orange (from Top500 data) and in blue (from Top8000) fill
      the allowed regions for AsN, His, Leu, and Phe/Tyr. Phe and Tyr were done
      together as no significant difference was detected between their distributions.
      The extensive areas in green are where the two systems both declare allowed 
      conformations.}
    \label{fig:outcounts}
\end{figure}
\newpage
\input{out_8000_500}
\newpage
\input{frequency}
\newpage
\input{chis_and_angles}
\newpage
%\input{pdbchains}
